6CCS3PRJ \\\vspace{0.5cm} A Pragmatic Infrastructure Modelling and Verification Framework

### 2014-04-21 paper.tex
Hide perf testing for now
Added root cause analysis section

@@

\section{Performance Benchmarking}
\section{Real World Usage}

>>>>

\pagebreak
\subsection{Root Cause Analysis - Reachability Matrix}

As the Management API tracks dependencies between services and components, it is able to infer the likely root-cause of a problem.

The root cause is inferred via the following process:

\begin{enumerate}
  \item Failing services and components are detected and raised in an incident.
  \item A reachability matrix is calculated via a recursive SQL query. The results of this query (a transitive closure\footnote{A transitive closure is defined as follows: http://mathworld.wolfram.com/TransitiveClosure.html}) can be used to check if there exists a path between two given nodes.

    This query can become expensive, with a time complexity on the order of $O(n^3)$, therefore it uses a common time-space tradeoff technique known as `materialized views'\footnote{For more details on materialized views, see http://www.postgresql.org/docs/9.3/static/rules-materializedviews.html} to incrementally compute changes over time. The total number of nodes is usually low enough to make this feasible.
  \item The failing service or component is defined as the root cause if:
    \begin{enumerate}
      \item It has no failing dependencies itself.
      \item There is a dependency path to it from all other failing services/components.
    \end{enumerate}
\end{enumerate}

As a concrete example, consider the following scenario:

\begin{figure}[!htbp]
  \centering
  \includegraphics[scale=0.7]{web-ui/rca.png}
\end{figure}

The component `Redis' is inferred as the root-cause, as all other failing components are dependent upon it, and it does not itself have any failing dependencies.

@@

%\section{Performance Benchmarking}
%\label{performance}
\section{Real World Usage}
